---
title: "ERCC2"
author: "jerod"
date: "June 28, 2016"
output: html_document
---

This analysis automates the map/build/analysis of ERCC2.0 reference datasets.
Most of the compute is intended to be performed on the cloud via predeveloped 7BG pipelines.
This is streamlined by the utilization of the API from R.
#Step 1:  Upload
First we need to know where your files are.  We assume they're present in a directory
called 'fastq' underneath the working directory
```{r}
fastqdir<-"fastq/"
fastqlist<-list.files(path = fastqdir,pattern = ".fastq*")
```
Second we need to collect some metadata.  Fill out the table metadatatable.txt with information
appropriate to your site:

```{R}

```

Then we need to upload them to the cloud for processing.  Auto-Upload is causing an issue.
```{r, echo=FALSE}
fastqmetadata<-read.table(file="metadatatable.txt",sep="\t",stringsAsFactors = FALSE,header = TRUE)
##my api token.  Will need to update before doing any major processing [but should be okay for this 1 HS run]
require(sevenbridges)
sevenbridgesapitoken="68916d51f8ba48c1a87a47f135bafef0"
authurl="https://api.sbgenomics.com/v2/" #i think...
a<-Auth(sevenbridgesapitoken,url=authurl)
p<-a$project(name = "prototypeercc2")

require("devtools")||install.packages("devtools");require("devtools")
require("sevenbridges")#available on bioconductor
for(fastq in fastqlist){
p$upload(filename = fastq,metadata=)
}
#check that the file was successfully uploaded
```
