---
title: "ERCC2"
author: "jerod"
date: "June 28, 2016"
output: html_document
---

This analysis automates the map/build/analysis of ERCC2.0 reference datasets.
Most of the compute is intended to be performed on the cloud via predeveloped 7BG pipelines.
This is streamlined by the utilization of the API from R.
#Step 1:  Upload
First we need to know where your files are.  We assume by default that they're present 
in a directory called 'fastq' underneath the working directory and that they are named 
in a way that is unique to your experiment.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(cache = TRUE)#better to not repeat
```

```{r}
#fastqdir<-"fastq/"
fastqdir<-"/Volumes/Archive2b/RawData/HSMagicMix/fastq/"
fastqlist<-list.files(path = fastqdir,pattern = ".fastq*")
erccproject="prototypeercc2"
```
Second we need to collect some metadata.  
Fill out the table metadatatable.txt with information appropriate to your site:

```{r}
fastqmetadata<-read.table(file="metadatatable.txt",sep=",",stringsAsFactors = FALSE,header = TRUE,colClasses = c(rep("character",10)))
#apparently everything's supposed to be a string.
head(fastqmetadata)
```

Then we need to upload them to the cloud for processing.  
```{r, echo=FALSE}
##my api token. [ should be okay for this 1 HS run]
require("sevenbridges")#available on bioconductor -- we're hoping to make this all as a pre-setup VM...
sevenbridgesapitoken="68916d51f8ba48c1a87a47f135bafef0"
authurl="https://api.sbgenomics.com/v2/"
a<-Auth(sevenbridgesapitoken,url=authurl)
p<-a$project(name = erccproject)

require("devtools")||install.packages("devtools");require("devtools")
upload2sbc<-function(fastqlist,fastqdir,fastqmetadata,project=p){
  lapply(fastqlist,uploadfile,project=project)
uploadfile<-function(fastq,project){
  if(is.null(project$file(name=fastq)))#only upload if it's not already in the cloud folder.  Tested, working.  
    {
    #actually check that the file was successfully uploaded
    #wrap this in try so that when it has errors [as it invariably will], it doesn't cancel everything.
    try(project$upload(filename = paste0(fastqdir,fastq)))
    if(!is.null(project$file(name=fastq))){
      if(project$file(id=project$file(name=fastq)$id)$size!=as.numeric(file.info(paste0(fastqdir,fastq))[1])){ #if the local size isn't the remote size, try again.
        fid=project$file(name=fastq)$id
        browser()#for testing.  Apparently not covered.
        project$file(id=fid)$delete #important to make sure that when you make a 'delete' call, it's to the file and not to the project...
        try(project$upload(filename = paste0(fastqdir,fastq)))
        }
      }
    }
  }

}

#actually call uploadfunction
#not run yet...
#uploadfunction(fastqlist,fastqdir,fastqmetadata,p)
```
Then we need to set the metadata on 7bc
```{R} 
lapply(fastqlist,updatemetadata,p=p)
updatemetadata<-function(x,p){
metadata<-fastqmetadata[fastqmetadata[,1]==x,2:length(fastqmetadata)]
p$file(name=x,exact = TRUE)$setMeta(as.list(metadata)) #actually works now that the formatting in metadatatable is correct
}