---
title: "ERCC2"
author: "jerod"
date: "June 28, 2016"
output: html_document
---

This analysis automates the map/build/analysis of ERCC2.0 reference datasets.
Most of the compute is intended to be performed on the cloud via predeveloped 7BG pipelines.
This is streamlined by the utilization of the API from R.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(cache = TRUE)#better to not repeat
```

#Step 1:  Define Inputs
We need 3 input arguments from you.

First we need to know where your files are.  We assume by default that they're 
present in a directory called 'fastq' underneath the working directory and that
they are named in a way that is unique to your experiment. Set this to fastqdir.

```{r}
# Edit next line to be your fastqdir:
# fastqdir<-"fastq/"
fastqdir <-"/Volumes/Archive2b/RawData/HSMagicMix/fastq/"

# Get fastq list
fastqlist <- list.files(path = fastqdir,pattern = ".fastq*")
erccproject <-"prototypeercc2" 
# This project should probably be unique to each participating lab so as to avoid issues.
# EG: ERCC2-NIST
# EG: ERCC2-Agilent
# Project Setup
# Copy over all apps:
# Copy over the basic references.
```
Second we need to collect some metadata.  
You should have a file named metadatatable.txt with information appropriate to 
your site:

```{r}
# Import metadatatable.txt
source("ConvenienceFunctions.R") # Functions that help the R interface with SBC go more smoothly and are applied in multiple contexts.
fastqmetadata <- read.table(file="metadatatable.txt",sep=",",stringsAsFactors = FALSE,header = TRUE,colClasses = c(rep("character",10)))
head(fastqmetadata)
```
Third, we need your sevenbridges token.  At this point, it's probably a good plan to tell you to change your email settings on sevenbridges:
You're going to get a *lot* of emails for successful runs if not.
```{r}
require("devtools")||install.packages("devtools");require("devtools")
require("sevenbridges")#available on bioconductor -- we're hoping to make this all as a pre-setup VM...
# Change this token, currently it's useless.
sevenbridgesapitoken="68916d51f8ba48c1a87a47f135bafef0"
```

#Step 2: Upload
Then we need to upload them to the cloud for processing.  
```{r, echo=FALSE}
authurl="https://api.sbgenomics.com/v2/"
a<-Auth(sevenbridgesapitoken,url=authurl)
p<-a$project(name = erccproject)

upload2sbc<-function(fastqlist,fastqdir,project=p){
  lapply(fastqlist,uploadfile,project=project)
uploadfile<-function(fastq,project){
  if(is.null(project$file(name=fastq)))#only upload if it's not already in the cloud folder.  
    {
    # Check that the file was successfully uploaded
    # Wrap this in try so that when it has errors [as it invariably will], it doesn't cancel everything.
    try(project$upload(filename = paste0(fastqdir,fastq)))
    if(!is.null(project$file(name=fastq))){
      if(project$file(id=project$file(name=fastq)$id)$size!=as.numeric(file.info(paste0(fastqdir,fastq))[1])){ # If the local size isn't the remote size, try again.
        fid=project$file(name=fastq)$id
        project$file(id=fid)$delete # Important to make sure that when you make a 'delete' call, it's to the file and not to the project...
        try(project$upload(filename = paste0(fastqdir,fastq)))
        }
      }
    }
  }
}

# Actually call uploadfunction
# Not run yet...
# uploadfunction(fastqlist,fastqdir,fastqmetadata,p)
```
Then we need to set the metadata on 7bc
```{R} 
lapply(fastqlist,updatemetadata,p=p)
```
