---
title: "02-CheckFQs"
author: "jerod"
date: "June 29, 2016"
output: html_document
---

Now we want to do some initial QC on the fastq files we just uploaded
```{r,echo=FALSE}
fastqdir="fastq/"
fastqlist<-list.files(path = fastqdir,pattern = ".fastq*")
```


```{r, echo=FALSE}
require(sevenbridges)
sevenbridgesapitoken="68916d51f8ba48c1a87a47f135bafef0"
authurl="https://api.sbgenomics.com/v2/" #i think...
a<-Auth(sevenbridgesapitoken,url=authurl)
p<-a$project(name = "prototypeercc2")
```


```{R, echo=FALSE}
#identify the app we're going to run [fastqc]
appid<-
  
  for(fastq in fastqlist){
  #get the 7bridges file id associated with it    
 
  #run the app on the fastq files 
tsk <- p$task_add(name = "FastQC Analysis", 
           description = "Run fastqc to check stuff", 
           app = appid,
           inputs = list(FASTQ_Reads=fastqid))
}
```

If we have to do any custom scripting or such, we just add it to docker and push that image:
http://docs.sevenbridges.com/docs/worked-example-of-uploading-a-custom-python-program

Would like to send all of the result plots to plotly because then we can compare across labs etc.  
It's open data, right?

Would also like to change the "html document" rendering options to utilize "code folding" because it's awesome.  
Once there are multiple sections at least.