---
title: "02-CheckFQs"
author: "jerod"
date: "June 29, 2016"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(cache = TRUE)
```

Now we want to do some initial QC on the fastq files we just uploaded
```{r,echo=FALSE}
#alternately, just search the project based on the metadata...
fastqmetadata<-read.csv("metadatatable.txt")
sbfastqlist<-lapply(fastqmetadata$Fastq.filename,FUN = function(x){findfile(name=x,p=p)})
```
```{r, echo=FALSE}
require(sevenbridges)
sevenbridgesapitoken="68916d51f8ba48c1a87a47f135bafef0"
authurl="https://api.sbgenomics.com/v2/" 
a<-Auth(sevenbridgesapitoken,url=authurl)
p<-a$project(name = "prototypeercc2",exact = TRUE)
```
```{R, echo=FALSE}
# identify the app we're going to run [fastqc]
appid<-p$app(name="FastQC Analysis")$id

fqcresult<-function(filename){
  # output filename of fastqc on a fastq input.  just a string modification
  return(gsub(x=filename,pattern = ".fastq[\\S]+",replacement="_fastqc.b64html",perl=TRUE))
}
  
  for(cfastq in sbfastqlist){
  # prepare to run the app on the fastq files 
  # check to see if the result file exists already
  if(is.null(findfile(fqcresult(cfastq$name),p))){  
tsk <- p$task_add(name = paste0("FastQC_",cfastq$name), 
           description = paste0("FastQC of ",cfastq$name), 
           app = appid,
           inputs=list(FASTQ_Reads = cfastq))
tsk$run() # actually run it
  }
  }
 # the expected result filename given an input fastq file.
```
Then we want to actually look at the results.  The output of fastqc is preconfigured to be
in HTML, so we just need to have a navbar that points to those files.

```{R}
# TODO Lindsay to figure out how to show the results of the fastqc run...
# output file for file.fastq is file_fastqc.b64html
# define a _site.yml & programatically write in the links [see https://rmarkdown.rstudio.com/rmarkdown_websites.html]
# test if the html files need to be downloaded to the /html folder for building or if they can be remote links
# also need to decide if / whether the output needs to be separate from the scripting of the runs.
# To download directly from R, use download call directly from single File object.
# findfile(name = "x",p)$download("~/Downloads/")
```
```{R}
# Define findfile function:   Searches sbc project for a file
# Avoids awkwardness around the default search only searching top100 files
findfile<-function(name,p,...){
  offset<-0
  while(length(p$file(offset=offset))==100){
    offset<-offset+100
  }# Count the total number of files
  maxoffset<-offset
  offset<-0
  while(offset <= maxoffset){
    if(!is.null(p$file(name=name,offset=offset))){return(p$file(name=name,offset=offset))}
    offset<-offset+100}
return(NULL)
} # findfile 
```

If we have to do any custom scripting or such, we just add it to docker and push that image:
http://docs.sevenbridges.com/docs/worked-example-of-uploading-a-custom-python-program

Would like to send all of the result plots to plotly because then we can compare across labs etc.  
It's open data, right?

Would also like to change the "html document" rendering options to utilize "code folding" because it's awesome.  
Once there are multiple sections at least.