---
title: "02-CheckFQs"
author: "jerod"
date: "June 29, 2016"
output: html_document
---

Now we want to do some initial QC on the fastq files we just uploaded
```{r,echo=FALSE}
fastqdir="fastq/"
fastqlist<-list.files(path = fastqdir,pattern = ".fastq*")
```


```{r, echo=FALSE}
require(sevenbridges)
sevenbridgesapitoken="68916d51f8ba48c1a87a47f135bafef0"
authurl="https://api.sbgenomics.com/v2/" #i think...
a<-Auth(sevenbridgesapitoken,url=authurl)
p<-a$project(name = "prototypeercc2")
```


```{R, echo=FALSE}
#identify the app we're going to run [fastqc]
tsk <- p$task_add(name = "runstuff", 
           description = "Generate some random number", 
           app = ,
           inputs = list(fastqid)))
```

If we have to do any custom scripting or such, we just add it to docker and push that image:
http://docs.sevenbridges.com/docs/worked-example-of-uploading-a-custom-python-program

Would like to send all of the result plots to plotly because then we can compare across labs etc.  
It's open data, right?

Would also like to change the "html document" rendering options to utilize "code folding" because it's awesome.  
Once there are multiple sections at least.